CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

\section{Approach}

>>>>

\section{TLA Specification}

\subsection{Experience with Apalache}

\subsection{Constraining TLC's Search Space}

We found four ways to cut down the state space in TLC:

\begin{itemize}
    \item \textbf{State constraints} are user-defined predicates.
    %
    If the predicate does not hold for a state, TLC does not explore any of its successors.

    \item \textbf{Symmetry sets} define equivalence classes between states.
    %
    Two states are considered equal if one can be transformed into the other by applying a permutation in the symmetry set.

    \item \textbf{Action constraints} are similar to state constraints, but refer to primed variables.
    %
    They are used to eliminate possible actions.
    %
    They can be emulated with state contraints and history variables, which we prefered.

    \item \textbf{Views} provide a way to change when TLC considers two states to be equal.
    %
    Two states are equal if their view evaluates to to the same value.
    %
    We use a view to instruct TLC to ignore history variables when comparing states.
    %
    This leads to a hundredfold decrease in number of states explored.

\section{Testing Approach}
